---
title: "Tutorial"
author: "Michael Rustler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Define config

```{r eval = FALSE}
config <- algoliar::create_config(app_id = "your_algolia_application_id",
                                  api_key = "your_algolia_api_key",
                                  index_name = "your_algolia_index_name",
                                  path_index_json = "path_to_your_index.json")

```

## Get

```{r eval = FALSE}
algoliar::algolia_get(config)

```

## Content

Content of "index.json" at Algolia as data.frame.

```{r eval = FALSE}
algoliar::algolia_content(config)
```

## Prepare Batch 

Preparing index.json so that it is accepted by Algolia for batch post (for 
details see: https://www.algolia.com/doc/api-reference/api-methods/add-objects/)

```{r eval = FALSE}
batch_json <- algoliar::prepare_batch_json(config)
```

## Run Batch 

For deleting/updating "index.json" at Algolia (for details see: https://www.algolia.com/doc/api-reference/api-methods/add-objects/)


```{r eval = FALSE}
algoliar::algolia_post_batch(batch_json, config)
```

This function is useful if the "index.json" upload to Algolia should be 
automated (i.e. after creating a new hugo academic website)

## Delete Index

For completly deleting an Algolia "index_name" run: 

```{r eval = FALSE}
algoliar::algolia_delete_index(config)
```

This means that it needs to be created manually again from the Algolia dashboard, 
since a creation method is not implemented in the R Package
